### 2016-08-16 rebuttal.tex

\pagebreak

\section{Comments from Editor}

\begin{questions}
\question I found the \url{http://live.sympy.org/} site very convenient for trying things
out in SymPy, but it is only mentioned in the supplement, which might be
overlooked by readers. I suggest moving that section into the main paper, as
it provides a great way to play along with the examples while reading the
paper.
\begin{solution}
  % TODO
\end{solution}
\question The Basic Usage section omits what I think is an important point:
how does one distinguish between evaluating exp(1) in Python and exp(1) in
SymPy? In other words, how are symbolic constants specified?
\begin{solution}
  % TODO. I'm unclear what the editor is asking here.
\end{solution}
\question The first
thing I tried after seeing Table 2 (simplication functions) did not work:

\begin{verbatim}
>>> trigsimp (exp( Matrix(2, 2, [0, -y, y, 0])) )
\end{verbatim}
fails to recognize cos and
sin. Am I expecting too much?
\begin{solution}
  This indeed does not work. The implementation in \verb|trigsimp| primarily
  thus far has focused on transforming trigonometric functions into other
  trigonometric functions. The ability to simplify complex exponentials is
  something that we would like to work.
  \href{https://github.com/sympy/sympy/issues/11459}{Issue 11459} in our
  public issue tracker tracks this feature.
\end{solution}
\question Section 3.6: are eigenvalues and singular
values included? If not, why not?
\begin{solution}
Yes, included.  Second example in that section address computation of
eigenvalues.  Let us know if we should expand this.
\end{solution}
\question Like one of the referees, I expected to
see MPFR mentioned in Section 4.1, at least to mention the pros and cons and
say why it isn't used.
\begin{solution}
  % TODO
\end{solution}
\question Section 4.1: please state whether the syntax for
functions in mpmath is identical, or not, to that in Sympy.
\begin{solution}
  % TODO
\end{solution}
\question Unless I have
missed something, a weakness of the paper is that speed is mentioned only
twice, on lines 496 and 666. My assumption is that SymPy is slow compared with
its commercial competitors. Please comment on the speed issue, and not just in
the conclusions.
\begin{solution}
  % TODO
\end{solution}
\question Editors are needed for [20].
\begin{solution}
  % TODO: I do not know how to make bibtex (with apalike) show the editor
  % here.
\end{solution}
\end{questions}

@@

This reads badly. Perhaps the following might be better?

This is due, in part, to the fact that the same language, Python, is used both for the internal implementation and the external usage by users.

\begin{solution}
We have changed the sentence as suggested.
\end{solution}
\question Line 221:
the phrase `Expression tree' is cited but this is not the first time you've used it. Perhaps cite earlier? Line 129 perhaps?

\begin{solution}
The footnote here was in reference to the SymPy classes. We have moved the
footnote later in the sentence, to ``\texttt{Basic}'', as suggested
by reviewer 3, point~\ref{rev3point16}.
\end{solution}
\question Page 8: Footnote 5
The line reads

@@

\begin{solution}
We have added a citation for mpmath.
\end{solution}
\end{questions}

\section{Reviewer 3 (Vedran Sego)}

\begin{questions}

\question Explaining what Python is (lines 70--72) should go before talking about SymPy as a ``CAS written in Python''. Further, the paper assumes a moderate familiarity with Python (for example, Python's console, OOP, and exceptions), and this should be specified. There should be a short note on the used Python console (\texttt{>>>} is the prompt, with the results of computation following immediately in the lines after it). The citation [25] from line 65 should be moved next to ``Python'' in line 70.
\begin{solution}
  % TODO: It seems better to start the paper with "SymPy is" rather than
  % "Python is". The reviewer perhaps wants us to not mention Python until the
  % second paragraph, but Python is important enough to SymPy's design that it
  % warrants mentioning in the first sentence, in my opinion. --Aaron
\end{solution}

@@

\question Line 73 has outdated information. Sage was renamed to SageMath and it no longer aims only at pure mathematics but also at algebra, numerical analysis, etc. The reference [40] should be replaced by a more up-to-date one.
\begin{solution}

\end{solution}

\question The plural ``CASs'' is usually written as ``CASes'' or ``CAS's'', with the latter being somewhat problematic due to it looking like it implies possession.
\begin{solution}
  % TODO: I recall we looked this up and the spelling consensus agreed with
  % the way we have it. We should double check (perhaps we can email the
  % editor to ask if the journal has a convention).
\end{solution}

\question Line 88 mentions ``printers'', but it doesn't state what they are, which is confusing for those readers that are yet to learn the concept in section 3.4.
\begin{solution}
We have changed ``printers'' to ``display formatters'', which is the
terminology used by Jupyter.
\end{solution}

\question Also in line 88, Jupyter's citation [30] is actually about IPython and should be replaced by a more up-to-date version.
\begin{solution}
We have changed the citation to

Kluyver, T., Ragan-Kelley, B., P{\'e}rez, F.,
Granger, B., Bussonnier, M., Frederic, J., Kelley,
K., Hamrick, J., Grout,
J., Corlay, S., et al. (2016). Jupyter notebooks---a publishing format for
reproducible computational workflows. In \textit{Positioning and Power in Academic
Publishing: Players, Agents and Agendas: Proceedings of the 20th International
Conference on Electronic Publishing}, page 87. IOS Press.

as recommended by the Jupyter developers at \url{https://github.com/jupyter/jupyter/issues/190}.
\end{solution}

\question The word ``software'' in line 91 is ambiguous; ``library'' or ``package'' would make a better choice.
\begin{solution}
We have changed ``software'' to ``library''.
\end{solution}

@@

\question Lines 91--96: ``we discuss/look at/etc'' is the preferred form, instead of ``section discusses/looks at/etc''.
\begin{solution}
  % TODO: We had decided not to use first person. We should perhaps email the editor
  % to ask about this.
\end{solution}

\question The paragraph in lines 103--105 should be moved to the introduction,
and the footnote from line 104 should be added to that paragraph as a
full-blown sentence, expanded by all the relevant technical information
(Python version, OS, \ldots). Given that the end of life for Python 2 is
2020., a comment on whether all the presented examples work in both Python 2
and 3 should be included as well. Further, emphasise that wildcard imports,
``\texttt{import *}'', should almost never be used in programs (see PEP 8, the
item ``wildcard imports''). The same goes for the \texttt{import} mentioned in lines 484--487.
\begin{solution}
We have moved the footnote inline, and have noted that the examples should
work with Python 2.7, 3.2, 3.3, 3.4, or 3.5, with any operating system that
supports Python.

We have added a footnote discussing the concerns with \texttt{import *} (see
reviewer 3, point~\ref{rev1point1}).
\end{solution}

@@

\end{solution}

\question There is no need to repeat ``(CAS)'' in line 124, as it was already given in line 64.
\begin{solution}

\end{solution}

\question In the same line, the word ``represents'' should be replaced by ``stores''.
\begin{solution}
  % I don't personally agree with this, but it's a minor point. --Aaron
\end{solution}

@@

\end{solution}

\question The code in line 210 should be made into its own line (like a displaymath formula), for typesetting reasons and better readability.
\begin{solution}

\end{solution}

\question The footnote 4 should be moved from line 221 to line 222, right after ``Basic''.
\label{rev3point16}
\begin{solution}
We have made the suggested change.
\end{solution}

### 2016-08-16 rebuttal.tex

\pagebreak

\section{Comments from Editor}

\begin{questions}
\question I found the \url{http://live.sympy.org/} site very convenient for trying things
out in SymPy, but it is only mentioned in the supplement, which might be
overlooked by readers. I suggest moving that section into the main paper, as
it provides a great way to play along with the examples while reading the
paper.
\begin{solution}
  % TODO
\end{solution}
\question The Basic Usage section omits what I think is an important point:
how does one distinguish between evaluating exp(1) in Python and exp(1) in
SymPy? In other words, how are symbolic constants specified?
\begin{solution}
  % TODO. I'm unclear what the editor is asking here.
\end{solution}
\question The first
thing I tried after seeing Table 2 (simplication functions) did not work:

\begin{verbatim}
>>> trigsimp (exp( Matrix(2, 2, [0, -y, y, 0])) )
\end{verbatim}
fails to recognize cos and
sin. Am I expecting too much?
\begin{solution}
  This indeed does not work. The implementation in \verb|trigsimp| primarily
  thus far has focused on transforming trigonometric functions into other
  trigonometric functions. The ability to simplify complex exponentials is
  something that we would like to work.
  \href{https://github.com/sympy/sympy/issues/11459}{Issue 11459} in our
  public issue tracker tracks this feature.
\end{solution}
\question Section 3.6: are eigenvalues and singular
values included? If not, why not?
\begin{solution}
Yes, included.  Second example in that section address computation of
eigenvalues.  Let us know if we should expand this.
\end{solution}
\question Like one of the referees, I expected to
see MPFR mentioned in Section 4.1, at least to mention the pros and cons and
say why it isn't used.
\begin{solution}
  % TODO
\end{solution}
\question Section 4.1: please state whether the syntax for
functions in mpmath is identical, or not, to that in Sympy.
\begin{solution}
The mpmath library is not a SymPy submodule, but a separate library,
that should be clear for a reader from the text.  From that, we believe,
it should obvious that in general syntax (i.e. names for special
functions, order of their arguments, etc) will be different, just
as for any other external library.
\end{solution}
\question Unless I have
missed something, a weakness of the paper is that speed is mentioned only
twice, on lines 496 and 666. My assumption is that SymPy is slow compared with
its commercial competitors. Please comment on the speed issue, and not just in
the conclusions.
\begin{solution}
  % TODO
\end{solution}
\question Editors are needed for [20].
\begin{solution}
  % TODO: I do not know how to make bibtex (with apalike) show the editor
  % here.
\end{solution}
\end{questions}

### 2016-08-16 architecture.tex
Move wildcard imports to the introduction
Also mention supported Python versions

The following statement imports all SymPy functions into the global Python
namespace.\footnote{\texttt{import *} has been used here to aid the
  readability of the paper, but is best to avoid such wildcard import
  statements in production code, as they make it unclear which names are
  present in the namespace. Furthermore, imported names could clash with
  already existing imports from another package. For example, SymPy, the
  standard Python \texttt{math} library, and NumPy all define the \texttt{exp}
  function, but only the SymPy one will work with SymPy symbolic expressions.}
From here on, all examples in this paper assume that this statement has been
executed.\footnote{All examples in this paper use SymPy version 1.0.}

\begin{verbatim}
>>> from sympy import *
\end{verbatim}

@@

Importantly, SymPy expressions are immutable. This simplifies the design of
SymPy by allowing expression interning. It also enables expressions to be
hashed and stored in Python dictionaries, thereby permitting features
such as caching.

>>>>

@@

Importantly, SymPy expressions are immutable. This simplifies the design of
SymPy by allowing expression interning. It also enables expressions to be
hashed and used as keys in Python dictionaries, thereby permitting features
such as caching.
